Prediction maps of defoliation at trees

### 2019-05-23 analysis/index.Rmd
wflow_publish(all = T)

[Report: Defoliation](defoliation-maps.html).

# 
Powered by [drake](https://github.com/ropensci/drake) + [workflowr](https://github.com/jdblischak/workflowr) and [mlr](https://github.com/mlr-org/mlr)

>>>>

- [Report: Defoliation](defoliation-maps.html)

# 
Powered by [drake](https://github.com/ropensci/drake) + [workflowr](https://github.com/jdblischak/workflowr) + [mlr](https://github.com/mlr-org/mlr)

### 2019-05-23 analysis/report-defoliation.Rmd
wflow_publish(all = T)

---
title: "Prediction maps of defoliation at trees"
output: 
  workflowr::wflow_html:
    css: style.css
    theme: readable
    number_sections: yes
    toc: yes
    toc_float: true
    toc_collapsed: true
    df_print: tibble
    includes:
      in_header: header.html
editor_options:
  chunk_output_type: console
author: "Patrick Schratz, Marc Becker, Friedrich-Schiller-University Jena"
---

>>>>

---
title: "Prediction maps of defoliation at trees"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
author: "Patrick Schratz, Marc Becker, Friedrich-Schiller-University Jena"
---
